A unified model for parsing and sentence understanding

### 2016-03-14 writing/hard_stack_paper/paper.tex
Pausing further paper work. Switching to eval stuff.

\begin{table*}[t]
  \centering\small
  \begin{tabular}{lcccc} 
    \toprule
Model                   & Params.    & Trans. acc.  &   Train  &   Test \\
\midrule
\multicolumn{5}{c}{Previous non-NN results}\\
\midrule
Lexicalized classifier \cite{snli:emnlp2015}
                        & --                & --                    &   99.7   &   78.2      \\
\midrule
\multicolumn{5}{c}{Previous sentence encoder-based NN results}\\
\midrule
100d LSTM encoders \cite{snli:emnlp2015}
                        & 221k               & --               &   84.8   &   77.6      \\
1024d pretrained GRU encoders \cite{DBLP:journals/corr/VendrovKFU15}
                        & 15m                & --              &   98.8   &   81.4       \\
300d Tree-based CNN encoders \cite{mou2015recognizing}
                        & 3.5m                & --             &   83.4   &   82.1       \\
\midrule
\multicolumn{5}{c}{Our results}\\
\midrule
300d LSTM RNN encoders          & 1.7m                  & --                &   83.9      &   80.6       \\
\result{300d PINN-Ext-NoTracking}   
                        & ?                  & --                &   ?      &   81.9dv       \\
\result{300d PINN-Ext }
                        & ?                  & --                &   ?      &   \underline{84.8dv}       \\
\result{300d PINN }
                        & ?                  & 92.2+dv            &   ?    &   83.3+dv       \\          
% \result{300d PINN-Ext, sequence-based attn.   }     
%                         & ?                  & --                &   ?      &   86.3dv         \\
% \result{300d PINN-Ext, tree-based attn. }           
%                         & ?                  & --                &   ?      &   \textbf{?}\\
\midrule
\multicolumn{5}{c}{Other previous NN results}\\
\midrule
100d LSTM w/ word-by-word attention \cite{rocktaschel2015reasoning}
                        & 252k               & --              &   85.3   &   83.5       \\
300d mLSTM word-by-word attention model \cite{DBLP:journals/corr/WangJ15b}
                        & 1.9m               & --             &   92.0   &   86.1      \\
300d LSTMN with deep attention fusion \cite{cheng2016long}
                        & 1.4m               & --                &   92.3   &   \textbf{89.1}      \\
    \bottomrule
  \end{tabular}
  \protect\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. Params. is the approximate number of trained parameters (excluding word embeddings for models where they are trained). Trans. acc. is the model's accuracy in predicting parsing transitions. Train and test are SNLI classification accuracy. \todo{[SB]: Estimate param counts as numbers come in.}} 
\end{table*}

@@

@@

\todo{[SB] Contrast sentence encoders w/ other models}

@@

We find that:
\begin{itemize}
\item Our PINN-Ext-NoTracking model precisely implements tree-structured compositionality (as in a TreeLSTM), but is capable of exploiting batched computation for dramatic \todo{[JG] Numbers} improvements in inference speed.
\item While the use of tree-structure alone does not offer a substantial improvement over an LSTM baseline, our tree-sequence hybrid model (PINN-Ext) substantially outperforms that baseline, suggesting that our model is able to successfully exploit tree structure, while using sequential context information to better resolve ambiguity.
\item It is possible to remove the dependence on an external parser from our model ...
\end{itemize}

>>>>

\begin{table*}[t]
  \centering\small
  \begin{tabular}{lcccc} 
    \toprule
Model                   & Params.    & Trans. acc.  &   Train  &   Test \\
\midrule
\multicolumn{5}{c}{Previous non-NN results}\\
\midrule
Lexicalized classifier \cite{snli:emnlp2015}
                        & --                & --                    &   99.7   &   78.2      \\
\midrule
\multicolumn{5}{c}{Previous sentence encoder-based NN results}\\
\midrule
100d LSTM encoders \cite{snli:emnlp2015}
                        & 221k               & --               &   84.8   &   77.6      \\
1024d pretrained GRU encoders \cite{DBLP:journals/corr/VendrovKFU15}
                        & 15m                & --              &   98.8   &   81.4       \\
300d Tree-based CNN encoders \cite{mou2015recognizing}
                        & 3.5m                & --             &   83.4   &   82.1       \\
\midrule
\multicolumn{5}{c}{Our results}\\
\midrule
300d LSTM RNN encoders          & 3.0m                  & --                &   83.9      &   80.6       \\
\result{300d PINN-Ext-NoTracking}   
                        & ?                  & --                &   ?      &   81.9dv       \\
\result{300d PINN-Ext }
                        & ?                  & --                &   ?      &   \underline{84.8dv}       \\
\result{300d PINN }
                        & ?                  & 92.2+dv            &   ?    &   83.3+dv       \\          
% \result{300d PINN-Ext, sequence-based attn.   }     
%                         & ?                  & --                &   ?      &   86.3dv         \\
% \result{300d PINN-Ext, tree-based attn. }           
%                         & ?                  & --                &   ?      &   \textbf{?}\\
\midrule
\multicolumn{5}{c}{Other previous NN results}\\
\midrule
100d LSTM w/ word-by-word attention \cite{rocktaschel2015reasoning}
                        & 252k               & --              &   85.3   &   83.5       \\
300d mLSTM word-by-word attention model \cite{DBLP:journals/corr/WangJ15b}
                        & 1.9m               & --             &   92.0   &   86.1      \\
300d LSTMN with deep attention fusion \cite{cheng2016long}
                        & 1.4m               & --                &   92.3   &   \textbf{89.1}      \\
    \bottomrule
  \end{tabular}
  \protect\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. Params. is the approximate number of trained parameters (excluding word embeddings for models where they are trained). Trans. acc. is the model's accuracy in predicting parsing transitions. Train and test are SNLI classification accuracy. \todo{[SB]: Estimate param counts as numbers come in.}} 
\end{table*}

@@

\todo{Note that the full PINN (i.e. Model 1) is in the same complexity class as PINN-Ext (what we're evaluating here) with very similar constants.}

@@

@@

We find that:
\begin{itemize}
\item Our PINN-Ext-NoTracking model precisely implements tree-structured compositionality (as in a TreeLSTM), but is capable of exploiting batched computation for dramatic \todo{[JG] Numbers} improvements in inference speed.
\item While the use of tree-structure alone does not offer a substantial improvement over an LSTM baseline, our tree-sequence hybrid model (PINN-Ext) substantially outperforms that baseline, suggesting that our model is able to successfully exploit tree structure, while using sequential context information to better resolve ambiguity.
\item It is possible to remove the dependence on an external parser from our model and replace it with a fast model-internal parser (as in the full PINN) with only a small decrease in model performance.
\end{itemize}
